Software Defect Prediction: Review, Commentary, and Future Work

### 2015-12-15 paper/paper.tex
Cliff's d

@@

\subsection{Context Factors}
Context factors for projects were assessed by Zhanget et al \cite{Zhang:2014:TBU:2597073.2597078}  Used as a measurement of project similarity. The provides a set of measurements to rank a project's relatedness when performing cross-project defect prediction.

>>>>

\subsection{Cliff's $\delta$}
Cliffs $\delta$ measures the effect size of the importance of the difference between two distributions. It is a nonparametric statistical test which represents the overlap two distributions. If two distributions are identical then the measurement is 0.  It was used by Zhang et al \cite{Zhang:2014:TBU:2597073.2597078} to determine the difference in the distributions of two project's metrics. If the difference of the effect size was large then the projects were not clustered together.  This was done as second step in clustering similar projects and only on project's whose Mann-Whitney U test determined a statistically significant difference.

@@

\subsection{Context Factors}
Context factors for projects were assessed by Zhang et et al \cite{Zhang:2014:TBU:2597073.2597078}  Used as a measurement of project similarity. The provides a set of measurements to rank a project's relatedness when performing cross-project defect prediction.
